Naturalness in U(1) extensions of the MSSM

### 2014-12-18 paper/e6ssm-tuning-paper.tex
half assed edit of caption, should add proper details later.
Added comments on the inert model.

Nonetheless the MSSM the impact of chargino limit is shown in
Fig. \cite{}.  There we see that if the the full parameter space with
$m_{\chi^\pm} < 700$ GeV was excluded the impact would be to make the
tuning in the MSSM with a $20$ TeV cuttoff slightly worse than that of
the E$_6$SSM with the same cuttoff and a $Z^\prime$ mass just larger
than current limits.  would be similar to that can also be attcked
more directly by looking at chargino mass limits as this rasies $\mu$
directly.  In the E$_6$SSM, while raising the chargino limit can have
the same impact in princuiple, due to current limits on the $Z^\prime$
mass already imposing a significant degree of tuning, chargino masses
do not make much of a noticable change.

@@

The exact level of tuning from the $Z^\prime$ depends on the charges of
the extra $U(1)$ gauge symmetry it is associated with.  In Fig.~\ref{}
we look at the fine tuning for other U(1) extensions for the same
$Z^\prime$ masses as we did for the E$_6$SSM.
% - plots for different U(1)' charge

@@

\begin{figure}[h]
\begin{center}
\resizebox{!}{5cm}{%
\includegraphics{e6inert_tb10_tuning_vs_higgs.png}}
\resizebox{!}{5cm}{%
\includegraphics{e6psi_tb10_tuning_vs_higgs.png}}\\
\resizebox{!}{5cm}{%
\includegraphics{e6eta_tb10_tuning_vs_higgs.png}}
\caption{Scatter plot of fine tuning vs lightest Higgs mass for the
  MSSM (green), E$_6$SSM with $M_{Z^\prime} = 2.5$ TeV (blue) and
  E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV (red).}
\label{Fig:e6ssmvsmssm}
\end{center}
\end{figure}

As can be seen in Fig.~\ref{} the severity of the tunings varies quite
a bit.  This is because the charges appear as coefficients in front of
the $Z^\prime$ mass in the EWSB condition.  These charges change the
value of the coefficient $d$ in Eq. (\ref{eq:originalE6MZequation}).
The values of the coefficient $d$ in each model, for $\tan\beta = 10$,
is $\{-0.01, 0.40, 0.50, 0.81 \}$ for $\{U(1)_I, U(1)_N, U(1)_\psi,
U(1)_\eta \}$ and this determines which of the models are most tuned.

>>>>

Nonetheless the MSSM the impact of chargino limit is shown in
Fig.~\ref{}.  There we see that if the the full parameter space with
$m_{\chi^\pm} < 700$ GeV was excluded the impact would be to make the
tuning in the MSSM with a $20$ TeV cuttoff slightly worse than that of
the E$_6$SSM with the same cuttoff and a $Z^\prime$ mass just larger
than current limits.  would be similar to that can also be attcked
more directly by looking at chargino mass limits as this rasies $\mu$
directly.  In the E$_6$SSM, while raising the chargino limit can have
the same impact in princuiple, due to current limits on the $Z^\prime$
mass already imposing a significant degree of tuning, chargino masses
do not make much of a noticable change.

@@

The exact level of tuning from the $Z^\prime$ depends on the charges
of the extra $U(1)$ gauge symmetry it is associated with.  In
Fig.~\ref{Fig:othere6modelsvsmssm} we look at the fine tuning for
other U(1) extensions for the same $Z^\prime$ masses as we did for the
E$_6$SSM.  To simplify the analysis we fix $\tan \beta = 10$, but scan
over the remaining parameters as in Table \ref{tab:scanranges} and fix
the rest to the same values we did in the scan carried out for
Fig.~\ref{Fig:e6ssmvsmssm}
% - plots for different U(1)' charge

@@

\begin{figure}[h]
\begin{center}
\resizebox{!}{5cm}{%
\includegraphics{e6inert_tb10_tuning_vs_higgs.png}}
\resizebox{!}{5cm}{%
\includegraphics{e6psi_tb10_tuning_vs_higgs.png}}\\
\resizebox{!}{5cm}{%
\includegraphics{e6eta_tb10_tuning_vs_higgs.png}}
\caption{Scatter plot of fine tuning vs lightest Higgs mass in ... with $M_{Z^\prime} = 2.5$ TeV shown in blue and $M_{Z^\prime} = 4.5$ TeV in red.}
\label{Fig:othere6modelsvsmssm}
\end{center}
\end{figure}

As can be seen in Fig.~\ref{Fig:othere6modelsvsmssm} the severity of the tunings varies quite
a bit.  This is because the charges appear as coefficients in front of
the $Z^\prime$ mass in the EWSB condition.  These charges change the
value of the coefficient $d$ in Eq. (\ref{eq:originalE6MZequation}).
The values of the coefficient $d$ in each model, for $\tan\beta = 10$,
is $\{-0.01, 0.40, 0.50, 0.81 \}$ for $\{U(1)_I, U(1)_N, U(1)_\psi,
U(1)_\eta \}$ and this determines which of the models are most tuned.

Interestingly the coefficient $d$ is very small (and negative) in the
case of the $U(1)_\eta$.  This allows a dramatic reduction in the fine
tuning from the $U(1)_I$ symmetry.  This is a result of the $H_u$
charge associated with $U(1)_I$ vansihing, which means that the
D-terms to the lightest Higgs which is predominantly $H_u$ at large
$\tan \beta$ are suppressed, making it difficult to raise the Higgs
mass in the same way as happens in the other models, explaining why
the heavier Higgs values are less well populated [can't be obtained? -
are we sure those scattered points are valid?]  than in the other
models.  Therefore the fine tuining behaviour in this model is closer
to that of the MSSM, though the LHC can still constrain the most
natural scenarions from just placing tougher limits on the $Z^\prime$
mass .
